Analyses

### 2021-04-24 src/analysis/Analysis.Rmd
update analysis file

```{r "Table with Descriptives"}
source(here("src/analysis/descriptive-information-overview.R"))
table2 <- knitr::kable(descr, digits=2)
fn <- here("report/figures/table_descriptives.md")
cat("# Table: Descriptive Information of Variables under Study \n\n", file=fn)
cat(table2, file=fn, sep="\n", append=T)

@@

## Intersection Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8, , eval = F}
source(here("src/analysis/h3.R"))
```

## Intersection Hypothesis -- Pooled
```{r "h3-pooled", fig.align="center", fig.height=8, fig.width=8, , eval = F}
source(here("src/analysis/h3-pooled.R"))
```

>>>>

```{r "Table with Descriptives"}
source(here("src/analysis/descriptive-information-overview.R"))
table2 <- knitr::kable(descr, digits=2)
fn <- here("report/figures/table_descriptives.tex")
cat("# Table: Descriptive Information of Variables under Study \n\n", file=fn)
cat(table2, file=fn, sep="\n", append=T)

@@

## Intersection Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8, eval = F}
source(here("src/analysis/h3.R"))
```

## Intersection Hypothesis -- Pooled
```{r "h3-pooled", fig.align="center", fig.height=8, fig.width=8, eval = F}
source(here("src/analysis/h3-pooled.R"))
```

## Exploration
